\chapter{The Q-Pix Digital Back-end}~\label{chap:qdb}

In Chapter~\ref{chap:qpix} we introduced the Q-Pix readout concept, where in Section~\ref{sec:digital_back-end} we introduced the concept of the digital back-end.
This chapter is dedicated to fully exploring the requirements of a Q-Pix digital back-end, where we discuss the design of the first digital prototypes to test this readout.

In Section~\ref{sec:digital_prototype} we describe the operating behavior of the first Q-Pix digital ASIC.
We describe the relevant communication procedures, configuration registers, and other design choices.
We complete the discussion of the prototype behavior in Section~\ref{sec:digital_fsm} where we describe the Finite-State Machine (FSM) and control logic of the ASIC.
Next, in Sections~\ref{sec:digital_problem} and~\ref{sec:digital_constraints} we introduce and discuss the design challenges required of the digital back-end.

Section~\ref{sec:calib} introduces a new calibration procedure for the digital readout.
We test this procedure on the first digital prototype boards presented in Section~\ref{sec:timing_test_results}.
Lattice Semiconductor FPGAs \citep{lattice_ice40up_datasheet} were selected because of the small form factor, pin out, availability, as well as low power consumption.
This calibration procedure is an essential capability to be able use free running oscillators in the Q-Pix readout to meet the timing requirements~\citep{qpix:nygren:mei}.

Finally, we conclude this chapter with a discussion on the the next steps to extend this readout into a DUNE-FD LArTPC.

The results presented in this chapter that are my individual work include the development of the prototype test boards, the soft-trigger and routing behavior of the digital ASIC, the development and verification of the calibration procedure, as well as the formalism to describe the collection of digital nodes.

\input{chapters/sub_chapters/qdb_part1.tex}

%% Part 2 begins here
\input{chapters/sub_chapters/qdb_part2.tex}